\textit{MSF: Modulated Sub-graph Finder}

### 2018-02-21 MSF_Paper_FA.tex
Updated contributions funding acknowledgments

The Ebola infection dataset analyzed during the current study are
available in the GEO repository, {\scriptsize
  https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE84188.}  The
network file used is from Reactome Functional interactions (FIs)
Version 2016

\subsection*{Author contributions}
In order to give appropriate credit to each author of an article, the individual
contributions of each author to the manuscript should be detailed in this section. We
recommend using author initials and then stating briefly how they contributed.

@@

\subsection*{Grant information}
Please state who funded the work discussed in this article, whether it is your employer,
a grant funder etc. Please do not list funding that you have that is not relevant to this
specific piece of research. For each funder, please state the funder’s name, the grant
number where applicable, and the individual to whom the grant was assigned.
If your work was not funded by any grants, please include the line: ‘The author(s)
declared that no grants were involved in supporting this work.’

\subsection*{Acknowledgements}
This section should acknowledge anyone who contributed to the research or the
article but who does not qualify as an author based on the criteria provided earlier
(e.g. someone or an organisation that provided writing assistance). Please state how
they contributed; authors should obtain permission to acknowledge from all those
mentioned in the Acknowledgements section.

@@

	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=10.0cm]{Git/MSF_Paper/Tgfb1} 
		\caption{}
	\end{subfigure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=10.0cm]{Git/MSF_Paper/TGFBstep1}
		\caption{}
	\end{subfigure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=10.0cm]{Git/MSF_Paper/TGFBstep2} 
		\caption{}
	\end{subfigure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=10.0cm]{Git/MSF_Paper/GFBstep3}
		\caption{}
	\end{subfigure}
	\caption{Overview of \texttt{MSF} process showing the steps to identify the modulated sub-graphs. (a) showing a network of genes with green nodes as genes with \textit{p}-values $< $ 0.05, and blue nodes are genes with \textit{p}-values $>$ 0.05, (b) the genes circled red show the two initial modulated sub-graphs, sub-graph1 found one with M,K,C and the second modulated sub-graph2 S,V,T, (c) shows the modulated sub-graph1 being extended to M,K,C,A,D, (d) shows both the modulated sub=paths merged with the addition of 3 genes Z,W,P.}
\end{figure*}

\begin{figure*}
	\centering
	\includegraphics[width=1.7\linewidth]{Git/MSF_Paper/Merged_Network}
	\caption{Modulated Sub-graph from 6hpi}
\end{figure*}

>>>>

The Ebola infection RNAseq dataset analyzed during the current study are
available in the GEO repository, {\scriptsize
  https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE84188.}  The cell signaling
network file used is from Reactome Functional interactions (FIs)
Version 2016

\subsection*{Author contributions}
FA proposed the idea. MF implemented the method. MF designed the benchmark
data set. MF analyzed the benchmark results. MF, FA, and IH contributed to
the manuscript writing. MF produced all figures. All authors read and
approved the final manuscript.

@@

\subsection*{Grant information}

This work was funded by the FWF (“Fonds zur Förderung der wissenschaftlichen Forschung”) within the project Internationalen Kooperationsprojektes - Intl cooperation Project (Joint Project - Lead Agency Verfahren) with the project number (I 1988-B22). The grant was assigned to Ivo Hofacker

\subsection*{Acknowledgements}

We thank all our colleagues who provided insight and expertise that greatly assisted the research and all reviewers for their constructive criticism.

\newpage

@@

	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=10.0cm]{Documents/PhDThesis/MSFPaper/Tgfb1} 
		\caption{}
	\end{subfigure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=10.0cm]{Documents/PhDThesis/MSFPaper/TGFBstep1}
		\caption{}
	\end{subfigure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=10.0cm]{Documents/PhDThesis/MSFPaper/TGFBstep2} 
		\caption{}
	\end{subfigure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=10.0cm]{Documents/PhDThesis/MSFPaper/TGFBstep3}
		\caption{}
	\end{subfigure}
	\caption{Overview of \texttt{MSF} process showing the steps to identify the modulated sub-graphs. (a) showing a network of genes with green nodes as genes with \textit{p}-values $< $ 0.05, and blue nodes are genes with \textit{p}-values $>$ 0.05, (b) the genes circled red show the two initial modulated sub-graphs, sub-graph1 found one with M,K,C and the second modulated sub-graph2 S,V,T, (c) shows the modulated sub-graph1 being extended to M,K,C,A,D, (d) shows both the modulated sub-graphs merged with the addition of 3 genes Z,W,P.}
\end{figure*}

\begin{figure*}
	\centering
	\includegraphics[width=1.6\linewidth]{ModulatesSubPaths/MSFData/Ebola6H/Merged_Network}
	\caption{Modulated Sub-graph from 6hpi}
\end{figure*}
